---
title: "Accessing PTMsToPathwaysData from ExperimentHub"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Accessing PTMsToPathwaysData from ExperimentHub}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = ">>")
```

This vignette shows how to find and download PTMsToPathways resources from
ExperimentHub once the records are available.

## Connect to ExperimentHub

```{r setup, eval = FALSE}
library(ExperimentHub)

eh <- ExperimentHub()
```

## Find PTMsToPathwaysData records

You can query directly:

```{r tag-query, eval = FALSE}
ptm_hub <- query(eh, "PTMsToPathwaysData")
ptm_hub
```

## Download a resource

Select an entry by index or by accession, then retrieve the object.

```{r download, eval = FALSE}
# Example: first matched record
obj1 <- ptm_hub[[1]]
```

## Inspect downloaded objects

```{r inspect, eval = FALSE}
class(obj1)
str(obj1, max.level = 1)
```

After a resource is downloaded once, ExperimentHub caches it locally and will
reuse the cached copy in later sessions.

## Session info
```{r session-info, eval = TRUE}
sessionInfo()
```